\sysfull

### 2017-08-11 paper/evaluation.tex
specified that compile time is in sec
2 figures replaced

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the dft application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compiler_result}. We used the {\tt time} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter than manual task splitting by a programmer (in  order of hours). For this reason we believe that \sys complier will be a major step in enabling computing community to enter the intermittent-power domain without big time investments.

@@

Figure~\ref{fig:page_size} presents the result on the effect of page swap size on the execution time of the programs executed by \sys. Overhead has been measured in the MCU clock cycles with values provided by TI CCS. Result has been normalized per benchmark: for the overhead results---to the minimum obtained value and for page faults---to the third measured maximum value. A subset of applications has been selected for evaluation. Additionally, page faults have been measured. The result show clearly a bathtub-shape bar plot for each application, demonstrating that for each application there is always a page size that minimizes \emph{both} execution time and page swaps. For all applications (except for Sort) this value equals roughly to 64 bytes. The shape of each figure can be explained as follows. For small page sizes (<64) the execution time is dominated by the \emph{frequency} of page swaps (each swap takes non-zero time, as shown in Figure~\ref{fig:dmaTimeEnergy}). On the other hand, in the opposite case the execution time is dominated by the time of swapping of one large page from SRAM to FRAM. Another interesting observation is the non-symmetric shape of each bar plot. This is due the size of data manipulated by the program: minimum point of overhead equals roughly to the size of the variables manipulated by each benchmark. Worth noting is also large discrepancy between minimum and maximum overhead for each benchmark (e.g. for Cuckoo 8 (at 16 bytes) to 1 (at 64 bytes), BC: 1 (at 16 bytes) to $\approx$2 (at 1024 bytes)).

>>>>

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the dft application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result in seconds are given in Table~\ref{table:compiler_result}. We used the {\tt time} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter than manual task splitting by a programmer (in  order of hours). For this reason we believe that \sys complier will be a major step in enabling computing community to enter the intermittent-power domain without big time investments.

@@

Figure~\ref{fig:page_size} presents the result on the effect of page swap size on the execution time of the programs executed by \sys. Overhead has been measured in the MCU clock cycles with values provided by TI CCS. Result has been normalized per benchmark: for the overhead results---to the minimum obtained value and for page faults---to the third measured maximum value. A subset of applications has been selected for evaluation. Additionally, page faults have been measured. The result show clearly a bathtub-shape bar plot for each application, demonstrating that for each application there is always a page size that minimizes \emph{both} execution time and page swaps. For all applications (except for Sort) this value equals roughly to 64 bytes. The shape of each figure can be explained as follows. For small page sizes (<64) the execution time is dominated by the \emph{frequency} of page swaps. On the other hand, in the opposite case the execution time is dominated by the time of swapping of one large page from SRAM to FRAM. Another interesting observation is the non-symmetric shape of each bar plot. This is due the size of data manipulated by the program: minimum point of overhead equals roughly to the size of the variables manipulated by each benchmark. Worth noting is also large discrepancy between minimum and maximum overhead for each benchmark (e.g. for Cuckoo 8 (at 16 bytes) to 1 (at 64 bytes), BC: 1 (at 16 bytes) to $\approx$2 (at 1024 bytes)).
